Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-07-26 paper_dev/article.tex
auto

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
%POLSAR data, like SAR, is stochastic.
%Moreover it is also multi-dimensional, making it even harder to interpret.
%It is therefore necessary to establish a simple and intuitive understanding of the data.
%Like SAR data, POLSAR data is stochastic.
%Moreover, it is multi-dimensional, making it even harder to interpret.
%Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
%Statistical models are undoubtedly crucial in understanding its stochastic nature.
While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional and stochastic nature of the data.
It is therefore necessary to establish a simple and intuitive model for the 
understanding of the data, and statistical models are undoubtedly suitable due to its stochastic nature.
Furthermore, practical POLSAR data processing also makes heavy use of scalar discrimination measures,
  which should be based on statistically consistent (i.e. signal-independent) models. %for scalar and representative observables of the multidimensional data.
It is thus important to establish scalar and representative observables for multi-dimensional POLSAR data.

@@

While these models undoubtedly help to further our understanding of POLSAR data,
  none of the underlying observables have been shown to meet the dual criteria of
  (i) resulting in statistically consistent discrimination measures and thus 
  (ii) being representative of the complex POLSAR data.

@@

Taking the log-transformation of the above equation, and denoting $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
{\small
\begin{align}
  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
\end{align}
}

@@

Upon setting $d=1$ into the above equations,
  the equations become:
\begin{align*}
  |C_v| &\sim  \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) \\ %\label{eqn:determinant_distribution} %\\
  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
\end{align*}

@@

As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be expressed as:
\begin{align*}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
This, in essence, derives an exact statistical distribution for the likelihood test statistics (as opposed to an asymptotic distribution \cite{{Conradsen_2003_TGRS_4}}).

@@

To show the robustness of the proposed models, 
  their validations are also put to test on different types of POLSAR sensors.
Specifically in this paper, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
  a fine-quad single-look complex RADARSAT2 image ($L=1$) are used.
Since the determinant of the covariance matrix is only significant on multi-look data,
  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).

@@

Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
In the test, the intensity of single-channel SAR data (HH) for sample homogeneous areas in both datasets is extracted.
The histograms for both the intensity and intensity ratio %the log-distance and contrast
  are then plotted against the theoretical PDF given above.
%Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
In all cases, the good match between the actual data and model distribution lends support to the proposed model. %providing us a simple validation of the result.

>>>>

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
%POLSAR data, like SAR, is stochastic.
%Moreover it is also multi-dimensional, making it even harder to interpret.
%It is therefore necessary to establish a simple and intuitive understanding of the data.
%Like SAR data, POLSAR data is stochastic.
%Moreover, it is multi-dimensional, making it even harder to interpret.
%Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
%Statistical models are undoubtedly crucial in understanding its stochastic nature.
While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional and stochastic nature of the data \cite{Lee_1994_TGRS_1017, Lopez-Martinez_2003_TGRS_2232}.
It is therefore necessary to establish a simple and intuitive model for the 
understanding of the data, and statistical models are undoubtedly suitable due to its stochastic nature.
Furthermore, practical POLSAR data processing also makes heavy use of scalar discrimination measures,
  which should be based on statistically consistent (i.e. signal-independent) models. %for scalar and representative observables of the multidimensional data.
It is thus important to establish scalar and representative observables for multi-dimensional POLSAR data.

@@

While these models undoubtedly help to further our understanding of POLSAR data,
  none of the underlying observables have been shown to meet the dual criteria of
  (i) resulting in statistically consistent discrimination measures and thus 
  (ii) being representative of the complex POLSAR data.
This will be self-evident in the next section 
  which reviews existing scalar POLSAR discrimination measures.

@@

Taking the log-transformation of the above equation, and denoting $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
{\small
\begin{align}
  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} % \\
  % \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
\end{align}
}

@@

Upon setting $d=1$ into the above equations,
  the equations become:
\begin{align*}
  |C_v| &\sim  \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) \\ %\label{eqn:determinant_distribution} %\\
  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \frac{\chi(2L)}{\chi(2L)}
\end{align*}

@@

As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be expressed as:
\begin{align*}
  %\ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
%where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
This, in essence, derives an exact statistical distribution for the likelihood test statistics (as opposed to an asymptotic distribution \cite{{Conradsen_2003_TGRS_4}}).

@@

To show the robustness of the proposed models, 
  their validations are also put to test on different types of POLSAR sensors.
Specifically in this paper, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
  a fine-quad single-look complex RADARSAT2 image ($L=1$) of Murda Merbok (Malaysia) are used.
Since the determinant of the covariance matrix is only significant on multi-look data,
  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).

@@

Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
In the test, the intensity of single-channel SAR data (HH) for sample homogeneous areas in both datasets is extracted.
The histograms for both the intensity and intensity ratio %the log-distance and contrast
  are then plotted against the theoretical PDF given above.
%Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
The values of $L$ are $L=3.2752$ and $L=3.4241$ for the AIRSAR and RadarSat2 images respectively.   
In all cases, the good match between the actual data and model distribution lends support to the proposed model. %providing us a simple validation of the result.
